---
title: "HBase Improvements"
author: "Aaron Benz"
date: "02/13/2015"
output: html_document
runtime: shiny
---

## Improvements on Retrieving Data
```{r, echo=FALSE}
library(rhbase)
library(magrittr)
library(data.table)
connect <- hb.init()
inputPanel(
  selectInput("airport", label = "Airport:",
              choices = c("LAX","JFK")),
  
  selectInput("variables", label = "variables:",choices = c("gear","rpm","speed"), multiple = T, selected = "gear")
  
)
colspecs <- reactive(paste("test", input$variables, sep = "::"))
hbase_scan_output <- reactive(hb.scan(tablename = "Test", startrow = input$airport,end = paste0(input$airport,"z"),colspec =colspecs())$get())

# hb.scan("Test","LAX","LAXz","test::rpm")$get()[[1]]
```

###Original rHBase Format

```{r, echo = F}
renderPrint({
  x <- hbase_scan_output()
  lapply(x, function(i){
    i[[3]] <- lapply(i[[3]],function(x){
          lapply(x, function(x) data.table(list(setDT(x))))})
    i
  })[1:2]
  })
```

###New Tidyr Format

```{r,echo=F}
new_scan_output <- reactive(hb.pull(tablename = "Test",column_family = "test", start = input$airport, end = paste0(input$airport,"z"),columns = input$variables))
renderPrint({
  new_scan_output()
})

```



## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
# shinyAppDir(".",
#   options=list(
#     width="100%", height=550
#   )
# )
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



